Supplemental Materials

### 2024-07-05 products/manuscript/supplement/Supplemental_Materials.qmd
Updated supplemental
For Draft to advisor

```{r}
#| label: tbl-table5
#| tbl-cap: "Model 5"
#| echo: FALSE
table5 <- readRDS(here::here("results", "tables", "table_log1.rds"))
table_gt <- gtsummary::as_gt(table_log1)
table_gt |> gt::as_raw_html()
```

@@

```{r}
#| label: tbl-table6
#| tbl-cap: "Model 6"
#| echo: FALSE
table6 <- readRDS(here::here("results", "tables", "table_log2.rds"))
table_gt <- gtsummary::as_gt(table_log2)
table_gt |> gt::as_raw_html()
```

@@

```{r}
#| label: tbl-table7
#| tbl-cap: "Model 7"
#| echo: FALSE
table7 <- readRDS(here::here("results", "tables", "table_log3.rds"))
table_gt <- gtsummary::as_gt(table_log3)
table_gt |> gt::as_raw_html()
```

```{r}
#| label: tbl-table8
#| tbl-cap: "Model 8"
#| echo: FALSE
table8 <- readRDS(here::here("results", "tables", "table_log4.rds"))
table_gt <- gtsummary::as_gt(table_log4)
table_gt |> gt::as_raw_html()
```
In these two models, the only significant finding is the final logistic model, in which infants born to mixed-race mothers had 21% higher odds of being born with low birth weight compared to infants born to white mothers. The other models did not show significant results.

@@

```{r}
#| label: tbl-table5
#| tbl-cap: "Cross-Validation Model 1"
#| echo: FALSE
ML_cv1_metrics <- readRDS(here::here("results", "tables", "ML_cv1_metrics.rds"))
ML_cv1_metrics
```

```{r}
#| label: tbl-table6
#| tbl-cap: "Cross-Validation Model 2"
#| echo: FALSE
ML_cv2_metrics <- readRDS(here::here("results", "tables", "ML_cv2_metrics.rds"))
ML_cv2_metrics
```

```{r}
#| label: tbl-table7
#| tbl-cap: "Cross-Validation Model 3"
#| echo: FALSE
ML_cv3_metrics <- readRDS(here::here("results", "tables", "ML_cv3_metrics.rds"))
ML_cv3_metrics
```

```{r}
#| label: tbl-table8
#| tbl-cap: "Cross-Validation Model 4"
#| echo: FALSE
ML_cv4_metrics <- readRDS(here::here("results", "tables", "ML_cv4_metrics.rds"))
ML_cv4_metrics
```

>>>>

```{r}
#| label: tbl-table5
#| tbl-cap: "Model 5"
#| echo: FALSE
table5 <- readRDS(here::here("results", "tables", "table_log1.rds"))
table_gt <- gtsummary::as_gt(table5)
table_gt |> gt::as_raw_html()
```

@@

```{r}
#| label: tbl-table6
#| tbl-cap: "Model 6"
#| echo: FALSE
table6 <- readRDS(here::here("results", "tables", "table_log2.rds"))
table_gt <- gtsummary::as_gt(table6)
table_gt |> gt::as_raw_html()
```

@@

```{r}
#| label: tbl-table7
#| tbl-cap: "Model 7"
#| echo: FALSE
table7 <- readRDS(here::here("results", "tables", "table_log3.rds"))
table_gt <- gtsummary::as_gt(table7)
table_gt |> gt::as_raw_html()
```

```{r}
#| label: tbl-table8
#| tbl-cap: "Model 8"
#| echo: FALSE
table8 <- readRDS(here::here("results", "tables", "table_log4.rds"))
table_gt <- gtsummary::as_gt(table8)
table_gt |> gt::as_raw_html()
```
In these two models, the only significant finding is the final logistic model, in which infants born to mixed-race mothers had 21% higher odds of being born with low birth weight compared to infants born to white mothers. The other models did not show significant results.

@@

```{r}
#| label: tbl-table9
#| tbl-cap: "Cross-Validation Model 1"
#| echo: FALSE
ML_cv1_metrics <- readRDS(here::here("results", "tables", "ML_cv1_metrics.rds"))
ML_cv1_metrics
```

```{r}
#| label: tbl-table10
#| tbl-cap: "Cross-Validation Model 2"
#| echo: FALSE
ML_cv2_metrics <- readRDS(here::here("results", "tables", "ML_cv2_metrics.rds"))
ML_cv2_metrics
```

```{r}
#| label: tbl-table11
#| tbl-cap: "Cross-Validation Model 3"
#| echo: FALSE
ML_cv3_metrics <- readRDS(here::here("results", "tables", "ML_cv3_metrics.rds"))
ML_cv3_metrics
```

```{r}
#| label: tbl-table12
#| tbl-cap: "Cross-Validation Model 4"
#| echo: FALSE
ML_cv4_metrics <- readRDS(here::here("results", "tables", "ML_cv4_metrics.rds"))
ML_cv4_metrics
```
